SMT-Based Context-Bounded Model Checking for Embedded Systems: State of the Art and Future Trends

### 2016-03-20 paper.tex
fix references

There are several invariant generation algorithms that discover linear and polynomial relations among integer and real variables, in order to provide loop invariants and also to discover the memory ``shape'' in programming languages with pointers~\cite{pips:2013,Henry:2012}. The current literature also reports successful applications of \textit{k}-induction based verification algorithms for hardware and software systems using invariants generation and strengthening, mostly based on interval analysis. In particular, Gadelha {\it et al.}, Beyer {\it et al.}, and Brain {\it et al.} presented new verification algorithms for proving correctness of (a large set of) C programs, by mathematical induction, in a completely automatic way ({\it i.e.}, users do not need to provide the loop invariant)~\cite{Gadelha15,Beyer15,Brain15}.

@@

\bibitem{Kopetz11}
H.~Kopetz:
\newblock {\em Real-Time Systems - Design Principles for Distributed Embedded Applications}.
\newblock Real-Time Systems Series, Springer, ISBN 978-1-4419-8236-0, pp. 1--376, 2011.

\bibitem{xu15}
Xua X., Jiaa H., Wanga D., Yub D., Chiangc H.:
\newblock {\em Hierarchical energy management system for multi-source multi-product microgrids}
\newblock In: Renewable Energy, v. 78, pp. 621--630, 2015.

\bibitem{leeCPS}
Lee E.:
\newblock {\em Cyber-physical Systems: Design Challenges.} 
\newblock In: International Symposium on Object Oriented Real-Time Distributed Computing, pp. 363--369, 2008.

\bibitem{leeCPS2}
Lee E.:
\newblock {\em The Past, Present and Future of Cyber-Physical Systems: A Focus on Models}. 
\newblock In: Sensors 15(3): pp. 4837--4869, 2015.

\bibitem{groza2015formal}
Groza A., Letia I., Goron A., Zaporojan S.: 
\newblock {\em A formal approach for identifying assurance deficits in unmanned aerial vehicle software}
\newblock In: Progress in Systems Engineering, Springer, pp. 233--239, 2015.

\bibitem{Cordeiro09}
Cordeiro L., Fischer B., Chen H., Marques-Silva J.:
\newblock {\em Semiformal Verification of Embedded Software in Medical Devices Considering Stringent Hardware Constraints.} 
\newblock In: International Conference on Embedded Software and Systems, pp. 396--403, 2009.

\bibitem{munir}
Munir  S., Stankovic J. A., Liang C.-J. M., Lin S.:
\newblock {\em Cyber Physical System Challenges for Human-in-the-Loop Control}. 
\newblock In: 8th International Workshop on Feedback Computing, pp. 1--4, 2013.

\bibitem{Kroening15}
Kroening D., Liang L., Melham T., Schrammel P., Tautschnig M.:
\newblock {\em Effective Verification of Low-Level Software with Nested Interrupts}. 
\newblock In: Design, Automation and Test in Europe, pp. 229--234, 2015.

\bibitem{Biere99}
Biere A., Cimatti A., Clarke E., Zhu Y.:
\newblock {\em Symbolic Model Checking without BDDs}. 
\newblock In: Tools and Algorithms for Construction and Analysis of Systems, LNCS 1579, pp. 193--207, 1999.

\bibitem{Armando06}
Armando A., Mantovani J., Platania L.:
\newblock {\em Bounded Model Checking of Software Using SMT Solvers Instead of SAT Solvers}. 
\newblock In: {SPIN} Workshop on Model Checking Software, LNCS 3925, pp. 146-162, 2006.

\bibitem{Behrend15}
Behrend J., Lettnin D., Gruenhage A., Ruf J., Kropf T., Rosenstiel W.:
\newblock {\em Scalable and Optimized Hybrid Verification of Embedded Software}. 
\newblock In: J. Electronic Testing 31(2): pp. 151--166, 2015.

\bibitem{Lettnin09}
Lettnin D., Nalla P. K., Behrend J., Ruf J., Gerlach J., Kropf T., Rosenstiel W., Sch{\"o}nknecht V., Reitemeyer S.:
\newblock {\em Semiformal Verification of Temporal Properties in Automotive Hardware Dependent Software}. 
\newblock In: Design, Automation and Test in Europe, pp. 1214--1217, 2009.

\bibitem{handbook09}
Biere A., Heule M., van Maaren H., Walsh T., eds.:
\newblock {\em Handbook of Satisfiability}.
\newblock Volume 185 of Frontiers in Artificial Intelligence and Applications., {IOS} Press, 2009.

\bibitem{BarrettSST09}
Barrett C., Sebastiani R., Seshia S.A., Tinelli C.:
\newblock {\em Satisfiability Modulo Theories}. 
\newblock In: Volume 185 of Frontiers in Artificial Intelligence and Applications. IOS Press, pp. 825--885, 2009.

\bibitem{Clarke04}
Clarke E., Kroening D., Lerda F.:
\newblock {\em A Tool for Checking {ANSI-C} Programs.}
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems. LNCS 2988, Springer Berlin Heidelberg, pp. 168--176, 2004.

\bibitem{MerzFS12}
Merz F., Falke S., Sinz C.:
\newblock {\em {LLBMC}: Bounded Model Checking of {C} and {C++} Programs using a Compiler {IR}.}
\newblock In: International Conference on Verified Software: Theories, Tools, Experiments. LNCS 7152, pp. 146--161, 2012.

\bibitem{CordeiroF11}
Cordeiro L., Fischer B.:
\newblock {\em Verifying Multi-threaded Software using {SMT}-based Context-Bounded Model Checking.}
\newblock In: International Conference on Software Engineering. pp. 331--340, 2011.

\bibitem{Ivancic05}
Ivanicic F., Shlyakhter I., Gupta A., Ganai, M.K.:
\newblock {\em Model Checking {C} Programs using {F-Soft}.}
\newblock In: International Conference on Computer Design: VLSI in Computers and Processors, pp. 297--308, 2005.

\bibitem{Cordeiro12}
Cordeiro L., Fischer B., Marques{-}Silva J.:
\newblock {\em {SMT}-based Bounded Model Checking for Embedded {ANSI-C} Software}.
\newblock {IEEE} Trans. Software Eng. \textbf{38}(4), pp. 957--974, 2012.

\bibitem{Bradley07}
Bradley A., Manna Z.:
\newblock {\em The calculus of computation - decision procedures with applications to verification}. 
\newblock In: Springer, pp. I-XV, pp. 1--366, 2007.

\bibitem{Donaldson10}
Donaldson A., Kroening D., R{\"{u}}mmer P.:
\newblock {\em {SCRATCH}: A Tool for Automatic Analysis of {DMA} Races.}
\newblock In: ACM Symposium on Principles and Practice of Parallel Programming. ACM, pp. 311--312, 2011.

\bibitem{Kinductor}
Donaldson A., Haller L., Kroening D., R{\"{u}}mmer, P.:
\newblock {\em Software Verification using \textit{k}-Induction.}
\newblock In: International Conference on Static Analysis. LNCS 6887, pp. 351--368, 2011.

\bibitem{EenS03}
E{\'{e}}n, N., S{\"{o}}rensson, N.:
\newblock {\em Temporal Induction by Incremental {SAT} Solving.}
\newblock Electronic Notes in Theoretical Computer Science \textbf{89}(4), pp. 543 -- 560, 2003.

\bibitem{GrosseLD09}
Gro{\ss}e D., Le H., Drechsler R.:
\newblock {\em Induction-based Formal Verification of {SystemC TLM} Designs.}
\newblock In: International Workshop on Microprocessor Test and Verification, pp. 101--106, 2009.

\bibitem{Sheera00}
Sheeran M., Singh S., St{\aa}lmarck G.:
\newblock {\em Checking Safety Properties using Induction and a {SAT}-solver.}
\newblock In: International Conference on Formal Methods in Computer-Aided Design. Springer-Verlag, pp. 108--125, 2000.

\bibitem{pips:2013}
ParisTech M.:
\newblock {\em PIPS: Automatic Parallelizer and Code Transformation Framework.} 
\newblock Accessed 21 February 2016

\bibitem{Henry:2012}
Henry J., Monniaux D., Moy M.: 
\newblock {\em PAGAI: A Path Sensitive Static Analyser.} 
\newblock In: Electronic Notes in Theoretical Computer Science, pp. 15--25, 2012.

\bibitem{BeyerSVCOMP15}
D.~Beyer:
\newblock {\em Software Verification and Verifiable Witnesses - (Report on SV-COMP 2015).} 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 401-416, 2015.

\bibitem{Gadelha15}
Gadelha M., Ismail H., Cordeiro L.:
\newblock {\em Handling Loops in Bounded Model Checking of C Programs via \textit{k}-Induction.}
\newblock In: International Journal on Software Tools for Technology Transfer (to appear), 2015.
\newblock http://dx.doi.org/10.1007/s10009-015-0407-9

\bibitem{Brain15}
Brain M., Joshi S., Kroening D., Schrammel P.:
\newblock {\em Safety Verification and Refutation by k-Invariants and k-Induction.} 
\newblock In: International Symposium on Static Analysis, LNCS 9291, pp. 145--161, 2015.

\bibitem{Beyer15}
Beyer D., Dangl M., Wendler P.:
\newblock {\em Boosting \textit{k}-Induction with Continuously-Refined Invariants.}
\newblock In: International Conference on Computer-Aided Verification, LNCS 9206, pp. 622--640, 2015.

\bibitem{Rocha15}
Rocha H., Ismail H., Cordeiro L., Barreto R.:
\newblock {\em Model Checking Embedded C Software using \textit{k}-Induction and Invariants.}
\newblock V Brazilian Symposium on Computing Systems Engineering, pp. 90--95, 2015.

\bibitem{Brain15}
Brain M., Joshi S., Kroening D., Schrammel P.:
\newblock {\em Safety Verification and Refutation by k-Invariants and \textit{k}-Induction.}
\newblock In: International Symposium on Static Analysis, LNCS 9291, pp. 145--161, 2015.

\bibitem{Inverso14}
Inverso O., Tomasco E., Fischer B., La Torre S., Parlato G.:
\newblock {\em Bounded Model Checking of Multi-threaded C Programs via Lazy Sequentialization.}
\newblock In: International Conference on Computer-Aided Verification, LNCS 8559, pp. 585-602, 2014.

\bibitem{dsv_spin2015}
Ismail H., Bessa I., Cordeiro L., Lima Filho E., Chaves Filho J.:
\newblock {\em DSVerifier: A Bounded Model Checking Tool for Digital Systems}. 
\newblock In: International SPIN Symposium on Model Checking of Software, LNCS 9232, pp. 126--131, 2015.

\bibitem{ECBS13}
Ramalho M., Lopes M., Sousa F., Marques H., Cordeiro L., Fischer B.:
\newblock {\em {SMT-Based Bounded Model Checking of C++ Programs} }.
\newblock In: International Conference on Engineering of Computer-Based Systems, pp. 147--156, 2013.

\bibitem{Sousa15}
Sousa F., Cordeiro L., Lima Filho E.: 
\newblock {\em { Bounded Model Checking of C++ Programs Based on the Qt Framework.}} 
\newblock In: Global Conference on Consumer Electronics, pp. 179--180, 2015.

\bibitem{Pereira15}
Pereira P.  Albuquerque H., Marques H., Silva I., Carvalho C., Santos V., Ferreira R., Cordeiro L.: 
\newblock {\em Verifying CUDA Programs using SMT-Based Context-Bounded Model Checking.} 
\newblock In: ACM Symposium on Applied Computing, Software Verification and Testing Track, pp. 1648-1653, 2016.

\bibitem{morse15}
J.~Morse.
\newblock {\em {Expressive and Efficient Bounded Model Checking of Concurrent Software}}.
\newblock {University of Southampton, PhD Thesis}, 2015.

\bibitem{civl15}
Zheng M, Rogers M, Luo Z, Dwyer M, Siegel S.
\newblock {\em{{CIVL}: Formal Verification of Parallel Programs}}.
\newblock In: International Conference on Automated Software Engineering, pp. 830--835, 2015.

\bibitem{esbmc_controller}
Bessa I., Abreu R., Cordeiro L., Filho J.:
\newblock {\em {SMT-Based Bounded Model Checking of Fixed-Point Digital Controllers)}.}
\newblock In: Annual Conference of the Industrial Electronics Society, pp. 295--301, 2014.

\bibitem{esbmc_filter}
Abreu R., Cordeiro L., Filho E.:
\newblock {\em {Verifying Fixed-Point Digital Filters using SMT-Based Bounded Model Checking}.}
\newblock In: XXXI Brazilian Symposium on Telecommunications, 2013.
\newblock http://dx.doi.org/10.14209/sbrt.2013.57

\bibitem{JMorse15}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {Model Checking LTL Properties over ANSI-C Programs with Bounded Traces.}} 
\newblock In: Software and System Modeling 14(1): pp. 65--81, 2015.

\bibitem{Bessa16}
Bessa I., Ismail H., Cordeiro L., Chaves Filho J.:
\newblock {\em { Verification of Fixed-Point Digital Controllers Using Direct and Delta Forms Realizations.}} 
\newblock In: Design Automation for Embedded Systems (to appear), 2016.

\bibitem{MorseCNF13}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em Handling unbounded loops with {ESBMC} 1.20.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 7795, Springer Berlin Heidelberg, pp. 619--622, 2013.

\bibitem{MorseRCN014}
Morse J., Ramalho M., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {ESBMC} 1.22.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 8413, Springer Berlin Heidelberg, pp. 405--407, 2014.

\bibitem{KahlonWG09}
Kahlon V, Wang C, Gupta A.
\newblock {\em{Monotonic Partial Order Reduction: An Optimal Symbolic Partial Order
  Reduction Technique}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 5643, pp. 398--413, 2009.

\bibitem{Beyer14}
D.~Beyer 
\newblock {Status report on software verification - (competition summary {SV-COMP})}. 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 8413, pp. 373--388, 2014.

>>>>

There are several invariant generation algorithms that discover linear and polynomial relations among integer and real variables, in order to provide loop invariants and also to discover the memory ``shape'' in programming languages with pointers~\cite{pips:2013,Henry:2012}. The current literature also reports successful applications of \textit{k}-induction based verification algorithms for hardware and software systems using invariants generation and strengthening, mostly based on interval analysis. In particular, Gadelha {\it et al.}, Beyer {\it et al.}, and Brain {\it et al.} presented new verification algorithms for proving correctness of (a large set of) C programs, by mathematical induction, in a completely automatic way ({\it i.e.}, users do not need to provide the loop invariant)~\cite{Gadelha15,Beyer15,Brain15,Rocha15}.

@@

%1
\bibitem{Kopetz11}
H.~Kopetz:
\newblock {\em Real-Time Systems - Design Principles for Distributed Embedded Applications}.
\newblock Real-Time Systems Series, Springer, ISBN 978-1-4419-8236-0, pp. 1--376, 2011.

%2
\bibitem{xu15}
Xua X., Jiaa H., Wanga D., Yub D., Chiangc H.:
\newblock {\em Hierarchical energy management system for multi-source multi-product microgrids}
\newblock In: Renewable Energy, v. 78, pp. 621--630, 2015.

%3
\bibitem{leeCPS}
Lee E.:
\newblock {\em Cyber-physical Systems: Design Challenges.} 
\newblock In: International Symposium on Object Oriented Real-Time Distributed Computing, pp. 363--369, 2008.

%4
\bibitem{leeCPS2}
Lee E.:
\newblock {\em The Past, Present and Future of Cyber-Physical Systems: A Focus on Models}. 
\newblock In: Sensors 15(3): pp. 4837--4869, 2015.

%5
\bibitem{groza2015formal}
Groza A., Letia I., Goron A., Zaporojan S.: 
\newblock {\em A formal approach for identifying assurance deficits in unmanned aerial vehicle software}
\newblock In: Progress in Systems Engineering, Springer, pp. 233--239, 2015.

%6
\bibitem{Cordeiro09}
Cordeiro L., Fischer B., Chen H., Marques-Silva J.:
\newblock {\em Semiformal Verification of Embedded Software in Medical Devices Considering Stringent Hardware Constraints.} 
\newblock In: International Conference on Embedded Software and Systems, pp. 396--403, 2009.

%7
\bibitem{munir}
Munir  S., Stankovic J. A., Liang C.-J. M., Lin S.:
\newblock {\em Cyber Physical System Challenges for Human-in-the-Loop Control}. 
\newblock In: 8th International Workshop on Feedback Computing, pp. 1--4, 2013.

%8
\bibitem{Kroening15}
Kroening D., Liang L., Melham T., Schrammel P., Tautschnig M.:
\newblock {\em Effective Verification of Low-Level Software with Nested Interrupts}. 
\newblock In: Design, Automation and Test in Europe, pp. 229--234, 2015.

%9
\bibitem{Biere99}
Biere A., Cimatti A., Clarke E., Zhu Y.:
\newblock {\em Symbolic Model Checking without BDDs}. 
\newblock In: Tools and Algorithms for Construction and Analysis of Systems, LNCS 1579, pp. 193--207, 1999.

%10
\bibitem{handbook09}
Biere A., Heule M., van Maaren H., Walsh T., eds.:
\newblock {\em Handbook of Satisfiability}.
\newblock Volume 185 of Frontiers in Artificial Intelligence and Applications., {IOS} Press, 2009.

%11
\bibitem{BarrettSST09}
Barrett C., Sebastiani R., Seshia S.A., Tinelli C.:
\newblock {\em Satisfiability Modulo Theories}. 
\newblock In: Volume 185 of Frontiers in Artificial Intelligence and Applications. IOS Press, pp. 825--885, 2009.

%12
\bibitem{Armando06}
Armando A., Mantovani J., Platania L.:
\newblock {\em Bounded Model Checking of Software Using SMT Solvers Instead of SAT Solvers}. 
\newblock In: {SPIN} Workshop on Model Checking Software, LNCS 3925, pp. 146-162, 2006.

%13
\bibitem{Clarke04}
Clarke E., Kroening D., Lerda F.:
\newblock {\em A Tool for Checking {ANSI-C} Programs.}
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems. LNCS 2988, Springer Berlin Heidelberg, pp. 168--176, 2004.

%14
\bibitem{MerzFS12}
Merz F., Falke S., Sinz C.:
\newblock {\em {LLBMC}: Bounded Model Checking of {C} and {C++} Programs using a Compiler {IR}.}
\newblock In: International Conference on Verified Software: Theories, Tools, Experiments. LNCS 7152, pp. 146--161, 2012.

%15
\bibitem{CordeiroF11}
Cordeiro L., Fischer B.:
\newblock {\em Verifying Multi-threaded Software using {SMT}-based Context-Bounded Model Checking.}
\newblock In: International Conference on Software Engineering. pp. 331--340, 2011.

%16
\bibitem{Ivancic05}
Ivanicic F., Shlyakhter I., Gupta A., Ganai, M.K.:
\newblock {\em Model Checking {C} Programs using {F-Soft}.}
\newblock In: International Conference on Computer Design: VLSI in Computers and Processors, pp. 297--308, 2005.

%17
\bibitem{Cordeiro12}
Cordeiro L., Fischer B., Marques{-}Silva J.:
\newblock {\em {SMT}-based Bounded Model Checking for Embedded {ANSI-C} Software}.
\newblock {IEEE} Trans. Software Eng. \textbf{38}(4), pp. 957--974, 2012.

%18
\bibitem{EenS03}
E{\'{e}}n, N., S{\"{o}}rensson, N.:
\newblock {\em Temporal Induction by Incremental {SAT} Solving.}
\newblock Electronic Notes in Theoretical Computer Science \textbf{89}(4), pp. 543 -- 560, 2003.

%19
\bibitem{Sheera00}
Sheeran M., Singh S., St{\aa}lmarck G.:
\newblock {\em Checking Safety Properties using Induction and a {SAT}-solver.}
\newblock In: International Conference on Formal Methods in Computer-Aided Design. Springer-Verlag, pp. 108--125, 2000.

%20
\bibitem{Bradley07}
Bradley A., Manna Z.:
\newblock {\em The calculus of computation - decision procedures with applications to verification}. 
\newblock In: Springer, pp. I-XV, pp. 1--366, 2007.

%21
\bibitem{pips:2013}
ParisTech M.:
\newblock {\em PIPS: Automatic Parallelizer and Code Transformation Framework.} 
\newblock Accessed 21 February 2016

%22
\bibitem{Henry:2012}
Henry J., Monniaux D., Moy M.: 
\newblock {\em PAGAI: A Path Sensitive Static Analyser.} 
\newblock In: Electronic Notes in Theoretical Computer Science, pp. 15--25, 2012.

%23
\bibitem{Gadelha15}
Gadelha M., Ismail H., Cordeiro L.:
\newblock {\em Handling Loops in Bounded Model Checking of C Programs via \textit{k}-Induction.}
\newblock In: International Journal on Software Tools for Technology Transfer (to appear), 2015.
\newblock http://dx.doi.org/10.1007/s10009-015-0407-9

%24
\bibitem{Beyer15}
Beyer D., Dangl M., Wendler P.:
\newblock {\em Boosting \textit{k}-Induction with Continuously-Refined Invariants.}
\newblock In: International Conference on Computer-Aided Verification, LNCS 9206, pp. 622--640, 2015.

%25
\bibitem{Brain15}
Brain M., Joshi S., Kroening D., Schrammel P.:
\newblock {\em Safety Verification and Refutation by k-Invariants and \textit{k}-Induction.}
\newblock In: International Symposium on Static Analysis, LNCS 9291, pp. 145--161, 2015.

%26
\bibitem{Rocha15}
Rocha H., Ismail H., Cordeiro L., Barreto R.:
\newblock {\em Model Checking Embedded C Software using \textit{k}-Induction and Invariants.}
\newblock V Brazilian Symposium on Computing Systems Engineering, pp. 90--95, 2015.

%27
\bibitem{Donaldson10}
Donaldson A., Kroening D., R{\"{u}}mmer P.:
\newblock {\em {SCRATCH}: A Tool for Automatic Analysis of {DMA} Races.}
\newblock In: ACM Symposium on Principles and Practice of Parallel Programming. ACM, pp. 311--312, 2011.

%28
\bibitem{Kinductor}
Donaldson A., Haller L., Kroening D., R{\"{u}}mmer, P.:
\newblock {\em Software Verification using \textit{k}-Induction.}
\newblock In: International Conference on Static Analysis. LNCS 6887, pp. 351--368, 2011.

%29
\bibitem{Behrend15}
Behrend J., Lettnin D., Gruenhage A., Ruf J., Kropf T., Rosenstiel W.:
\newblock {\em Scalable and Optimized Hybrid Verification of Embedded Software}. 
\newblock In: J. Electronic Testing 31(2): pp. 151--166, 2015.

%30
\bibitem{Lettnin09}
Lettnin D., Nalla P. K., Behrend J., Ruf J., Gerlach J., Kropf T., Rosenstiel W., Sch{\"o}nknecht V., Reitemeyer S.:
\newblock {\em Semiformal Verification of Temporal Properties in Automotive Hardware Dependent Software}. 
\newblock In: Design, Automation and Test in Europe, pp. 1214--1217, 2009.

%31
\bibitem{GrosseLD09}
Gro{\ss}e D., Le H., Drechsler R.:
\newblock {\em Induction-based Formal Verification of {SystemC TLM} Designs.}
\newblock In: International Workshop on Microprocessor Test and Verification, pp. 101--106, 2009.

%32
\bibitem{BeyerSVCOMP15}
D.~Beyer:
\newblock {\em Software Verification and Verifiable Witnesses - (Report on SV-COMP 2015).} 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 401-416, 2015.

%33
\bibitem{Inverso14}
Inverso O., Tomasco E., Fischer B., La Torre S., Parlato G.:
\newblock {\em Bounded Model Checking of Multi-threaded C Programs via Lazy Sequentialization.}
\newblock In: International Conference on Computer-Aided Verification, LNCS 8559, pp. 585-602, 2014.

%34
\bibitem{dsv_spin2015}
Ismail H., Bessa I., Cordeiro L., Lima Filho E., Chaves Filho J.:
\newblock {\em DSVerifier: A Bounded Model Checking Tool for Digital Systems}. 
\newblock In: International SPIN Symposium on Model Checking of Software, LNCS 9232, pp. 126--131, 2015.

%35
\bibitem{ECBS13}
Ramalho M., Lopes M., Sousa F., Marques H., Cordeiro L., Fischer B.:
\newblock {\em {SMT-Based Bounded Model Checking of C++ Programs} }.
\newblock In: International Conference on Engineering of Computer-Based Systems, pp. 147--156, 2013.

%36
\bibitem{Sousa15}
Sousa F., Cordeiro L., Lima Filho E.: 
\newblock {\em { Bounded Model Checking of C++ Programs Based on the Qt Framework.}} 
\newblock In: Global Conference on Consumer Electronics, pp. 179--180, 2015.

%37
\bibitem{Pereira15}
Pereira P.  Albuquerque H., Marques H., Silva I., Carvalho C., Santos V., Ferreira R., Cordeiro L.: 
\newblock {\em Verifying CUDA Programs using SMT-Based Context-Bounded Model Checking.} 
\newblock In: ACM Symposium on Applied Computing, Software Verification and Testing Track, pp. 1648-1653, 2016.

%38
\bibitem{morse15}
J.~Morse.
\newblock {\em {Expressive and Efficient Bounded Model Checking of Concurrent Software}}.
\newblock {University of Southampton, PhD Thesis}, 2015.

%39
\bibitem{civl15}
Zheng M, Rogers M, Luo Z, Dwyer M, Siegel S.
\newblock {\em{{CIVL}: Formal Verification of Parallel Programs}}.
\newblock In: International Conference on Automated Software Engineering, pp. 830--835, 2015.

%40
\bibitem{esbmc_controller}
Bessa I., Abreu R., Cordeiro L., Filho J.:
\newblock {\em {SMT-Based Bounded Model Checking of Fixed-Point Digital Controllers)}.}
\newblock In: Annual Conference of the Industrial Electronics Society, pp. 295--301, 2014.

%41
\bibitem{esbmc_filter}
Abreu R., Cordeiro L., Filho E.:
\newblock {\em {Verifying Fixed-Point Digital Filters using SMT-Based Bounded Model Checking}.}
\newblock In: XXXI Brazilian Symposium on Telecommunications, 2013.
\newblock http://dx.doi.org/10.14209/sbrt.2013.57

%42
\bibitem{JMorse15}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {Model Checking LTL Properties over ANSI-C Programs with Bounded Traces.}} 
\newblock In: Software and System Modeling 14(1): pp. 65--81, 2015.

%43
\bibitem{Bessa16}
Bessa I., Ismail H., Cordeiro L., Chaves Filho J.:
\newblock {\em { Verification of Fixed-Point Digital Controllers Using Direct and Delta Forms Realizations.}} 
\newblock In: Design Automation for Embedded Systems (to appear), 2016.

%44
\bibitem{MorseCNF13}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em Handling unbounded loops with {ESBMC} 1.20.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 7795, Springer Berlin Heidelberg, pp. 619--622, 2013.

%45
\bibitem{MorseRCN014}
Morse J., Ramalho M., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {ESBMC} 1.22.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 8413, Springer Berlin Heidelberg, pp. 405--407, 2014.

%46
\bibitem{KahlonWG09}
Kahlon V, Wang C, Gupta A.
\newblock {\em{Monotonic Partial Order Reduction: An Optimal Symbolic Partial Order
  Reduction Technique}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 5643, pp. 398--413, 2009.

%47
\bibitem{Beyer14}
D.~Beyer 
\newblock {Status report on software verification - (competition summary {SV-COMP})}. 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 8413, pp. 373--388, 2014.
